\section{Vector Fields}

\subsection{Vector Fields and Flows, Divergence and Curl}
\paragraph{Flow Lines}
If \(F\) is a vector field, a flow line for \(F\) is a path \(c(t)\)
such that
\[c'(t) = F(c(t)).\]
That is, that \(F\) yields the velocity field of the path \(c(t)\).

\paragraph{The Del \(\grad\) operator}
The vector differential operator \(\grad\) may be considered a 
symbolic vector.
The differential operator may be written as 
\[\grad = \frac{\partial}{\partial x}i + \frac{\partial}{\partial y}j + \frac{\partial}{\partial z}k.\]

\paragraph{Divergence}
Given a field \(F = (f_1, f_2, \dots, f_n)\), the divergence of \(F\) is
\[\text{div} F = \div F = \sum_{i=1}^n \grad f_i.\]

Divergence may be thought as a type of derivative that describes the measure at which 
a vector field \textit{spreads away} from a certain point.
If the divergence is positive, then there is a net outflow while there is net inflow if the divergence is negative.

Observe that the divergence of a vector field will be real-valued.

\paragraph{Curl}
If \(F\) is a vector field, then the curl may be defined as
\[\mathrm{curl}F = \curl F.\]

Curl is also analogous to a type of derivative for vector fields. The curl may be though as the measure at which the vector field \textit{swirls} around a point.
A positive swirl can be thought of as a counter clockwise rotation.

Observe that the curl of a vector field is also a vector field.

\subsection{Vector Identities}


\paragraph{Basic Vector Identities}

\begin{enumerate}
    \item \(\grad(f + g) = \grad f + \grad g\)
    \item \(\grad (\lambda f) = \lambda \grad f\) where \(\lambda \in \mathbb{R}\)
    \item \(\grad (fg) = g \grad f + f \grad g\). You may draw analogies to the product.
    \item \(\grad \dfrac{f}{g} = \dfrac{f\grad g - g\grad f}{g^2}\) where \(g\neq 0\). This is analogous to the quotient rule.
    \item \(\div (F + G) = \div F + \div G\)
    \item \(\curl (F + G) = \curl F + \curl G\)
    \item \(\div (fF) = f\div F = F\cdot \grad f\)
    \item \(\div (F\times G) = G \cdot (\curl F) - F \cdot (\curl G)\)
    \item \(\div(\curl F) = 0\)
    \item \(\curl (fF) = f\curl F = \grad f \times F\)
    \item  \(\curl (\grad f) = 0\)
    \item \(\grad^2 (fg) = f\grad^2 g + 2((\grad f \cdot \grad g)) + g\grad^2f\)
    \item \(\div (\grad \times \grad g) = 0\)
    \item \(\div(f\grad g - g\grad f) = f\grad^2 g - g\grad f^2\)
\end{enumerate}
